OpenMPIR

### 2017-10-06 paper.tex
Fixed up paragraph in section 7.1

Putting failures aside, performance for our implementation is quite strong,
generally outperforming or matching the best of existing implementations. For
benchmarks where the overhead-to-work ratio is high is where the Tapir (and 
Cilk) implementation shows significant benefit. For example, for the \texttt{Fibonacci}
benchmark, our implementation runs significantly faster than any of the
others. While ICC failed for that size input, we did test with smaller inputs
and found it was similarly outperformed by the Tapir implementation.  \texttt{NQueens}
and \texttt{FFT} show similar behavior but to lesser degrees. In contrast,
benchmarks that have a lower overhead to work ratio unsurprisingly differ less
in performance. For example,

%%% something missing here!

>>>>

Putting failures aside, performance for our implementation is quite strong,
generally outperforming or matching the best of existing implementations. For
benchmarks where the overhead-to-work ratio is high is where the Tapir + Cilk
implementation shows significant benefit. For example, for the
\texttt{Fibonacci} benchmark, our implementation runs significantly faster than
any of the others. \texttt{NQueens} and \texttt{FFT} show similar behavior but
to lesser degrees. In contrast, benchmarks that have a lower overhead to work
ratio unsurprisingly differ less in performance.
